---
title: "Validation of graph correction"
output:
  html_document:
    toc: true
  html_notebook: default
---

## Подключаем требуемые пакеты

```{r, message=FALSE, warning=FALSE}
library(igraph)
library(pagoda2)
library(ggplot2)
library(magrittr)
library(Pagoda2GraphImprovement)

theme_set(theme_bw())

set.seed(2018)
```

## Считываем данные и граф

```{r}
path_floder <- DataPath("filtered_gene_bc_matrices/GRCh38")

load_matrix <- pagoda2::read.10x.matrices(path_floder)
load_matrix <- load_matrix[!duplicated(rownames(load_matrix)),]
pagoda_data <- pagoda2::basicP2proc(load_matrix)

lst <- readRDS(rprojroot::is_r_package$find_file("output/validation.rds"))
umap_raw <- lst$umap_raw
umap_corrected <- lst$umap_corrected
clusters_corrected <- lst$clusters_corrected
clusters_raw <- lst$clusters_raw
all_clusters <- lst$all_clusters
```

## Validation

```{r}
plot_mtx <- as.matrix(pagoda_data$counts) %>% apply(2, function(v) scales::rescale(rank(v)))
```

```{r}
conos::embeddingPlot(umap_raw, groups=all_clusters)
conos::embeddingPlot(pagoda_data$embeddings$PCA$tSNE, groups=all_clusters)
```

### Raw

```{r}
conos::embeddingPlot(pagoda_data$embeddings$PCA$tSNE, groups=clusters_raw, title="Raw t-SNE")
conos::embeddingPlot(umap_corrected, groups=clusters_raw, title="Corrected")
```

#### Clusters 8, 10, 11, 16

```{r, fig.width=8, fig.height=5}
c("CMC1", "GZMH", "TRGC2", "CD8A", "TRAC", "PFN1") %>% 
  lapply(PlotEmbeddingGeneFraction, pagoda_data$embeddings$PCA$tSNE, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=3)
```

```{r, fig.width=8, fig.height=5}
c("CMC1", "GZMH", "TRGC2", "CD8A", "TRAC", "PFN1") %>% 
  lapply(PlotEmbeddingGeneFraction, umap_corrected, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=3)
```

On corrected data we still can see some level of separation, but it's much worse.

#### Clusters 5, 13, 15

```{r, fig.width=8, fig.height=8}
c("FOS", "JUN", "UBC", "DUSP2", "RPS3", "ACTB", "H3F3A", "PFN1", "MALAT1") %>% 
  lapply(PlotEmbeddingGeneFraction, pagoda_data$embeddings$PCA$tSNE, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=3)
```

```{r, fig.width=8, fig.height=8}
c("FOS", "JUN", "UBC", "DUSP2", "RPS3", "ACTB", "H3F3A", "PFN1", "MALAT1") %>% 
  lapply(PlotEmbeddingGeneFraction, umap_corrected, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=3)
```

So we have almost the same level of separateon on raw and corrected clusters

#### Clusters 1, 12, 14

```{r, fig.width=12, fig.height=8}
c("S100A8", "S100A12", "CD14", "MS4A6A", "CD74", "HLA-DPB1", "FCER1A", "RPL15", "FCGR3A", "RPS19", "COTL1", "RHOC") %>% 
  lapply(PlotEmbeddingGeneFraction, pagoda_data$embeddings$PCA$tSNE, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=4)
```

```{r, fig.width=12, fig.height=8}
c("S100A8", "S100A12", "CD14", "MS4A6A", "CD74", "HLA-DPB1", "FCER1A", "RPL15", "FCGR3A", "RPS19", "COTL1", "RHOC") %>% 
  lapply(PlotEmbeddingGeneFraction, umap_corrected, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=4)
```

Corrected looks better

### Corrected

```{r}
conos::embeddingPlot(pagoda_data$embeddings$PCA$tSNE, groups=clusters_corrected, title="Raw t-SNE, new clusters")
conos::embeddingPlot(umap_corrected, groups=clusters_corrected, title="Corrected, new clusters")
```

#### Clusters 2, 10, 19-23

```{r, fig.width=12, fig.height=3}
c("CD52", "FAM26F", "RHOC", "TUBA1B") %>% 
  lapply(PlotEmbeddingGeneFraction, umap_corrected, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=4)
```

2: CXCL8, JUND, S100A12, NFKBIA, RPL39, VCAN

10: RPL6, RPL7A, RPL15, RPS17 (not seen in raw data)
11: CD52, FAM26F, RHOC, TUBA1B

19: CD79B, MS4A1, IGKC
20: B2M, RNASET2, FOSB, ANXA1, KLF6 (not really seen in raw data)
21: TRAC, TRBC2, IL32
23: SDPR, GNG11, PF4, CD9, PPBP

Raw data:

```{r, fig.width=12, fig.height=3}
c("PF4", "CD9", "PPBP") %>% 
  lapply(PlotEmbeddingGeneFraction, pagoda_data$embeddings$PCA$tSNE, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=4)

c("CD52", "FAM26F", "RHOC", "TUBA1B") %>% 
  lapply(PlotEmbeddingGeneFraction, pagoda_data$embeddings$PCA$tSNE, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=4)

c("RNASET2", "FOSB", "ANXA1", "KLF6") %>% 
  lapply(PlotEmbeddingGeneFraction, pagoda_data$embeddings$PCA$tSNE, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=4)

c("RPL6", "RPL7A", "RPL15", "RPS17") %>% 
  lapply(PlotEmbeddingGeneFraction, pagoda_data$embeddings$PCA$tSNE, plot_mtx) %>% 
  cowplot::plot_grid(plotlist=., ncol=4)
```

